\section{The Employees}

You can find all the important employees on the org chart, but we listed them here with a short description of their skills and their roles in the company.
\\

\subsection{Christian - Head of IT}

He are responsible for IT as a department head. 
In his position he is involved in various projects and is also responsible for backups, project management, testing of new applications and security.
\\

He supervises Max and Sergio.

\subsection{Max - IT staff}

He works as a second and third level support.
He also has more to do with the system and therefore provides support to internal staff and work more with external partners.

\subsection{Sergio - IT staff}

He works as a system administrator primarily in first level support and also second level. He is also responsible for the implementation of projects in cooperation with the project manager.
He has close contact with the other employees.

\subsection{Susie - Head of accounting}

She is the head of the accounting department and is responsible for 30 employees. 
In this position she also works closely with the CEO.

\subsection{George - Accounting staff}

He is an accountant in the company. 
In this position, he has a lot of contact with clients and has to communicate with them regularly through different communication channels. 

\subsection{Stefania - CEO}

She is the CEO of the company and responsible for everything related to the company. 
Therefore, she has to make decisions, ensure the company has a good image and is in a good position for the different stakeholders.

As a CEO she is in close contact with the leadership of the different departments.
She has good relations with the IT and the accounting department, but does not really know the employees who work for these departments on a personal level.