\section{The Company}

Your players work in a company called \enquote{Field Castle Financial}.
 It's a company that handles tax reports for its customers, which consist of private clients and smaller companies.
They have a small IT brigade consisting of two coworkers and one head of IT.
\\

The accounting department makes up most of the workers, with 37 employees.
The company employs 45 people, including the CEO, assistants and HR.
\\

Your players will play certain employees of this company, while you will guide them.
It is up to you if you want to play one of the roles yourself, though we do not advise you to do so unless you are short on participants.
It will increase your workload during the game, and you will need to make sure not to overshare what you know in your role as an employee.
(You should not let the information you know from a GM perspective transfer to your role.)
\\

The company has a few issues which are not ideal for a good security policy:

\begin{itemize}
    \item Some systems aren't patched to the latest version, due to anxiety about backward compatibility with their financial software.
    \item The company website openly displays the whole hierarchy, with all coworkers and their contact details, making it fairly easy to gather OSINT.
    \item The backups have never been properly tested since there has never been a bigger incident that would have necessitated it.
\end{itemize}

The following infographic will give you an overview over the key metrics of the company: