\chapter{Introduction}

Hello, and welcome to this SecureRole role-playing game experience.
You have chosen to be a game master, also called \enquote{GM}.
If this is not the case, you have the wrong document.
\\

\begin{hint}[Important Information]
    This is a \enquote{Important Information} box, when ever you spot these, it means that this is crucial information for the success of this game.
    \textbf{Read it carefully!}
\end{hint}

\begin{hint}[Important Information]
    What is your responsibility as GM?
    Well, similar to a classic pen-and-paper game like Dungeons and Dragons, you will guide the players through this experience.
    You will have all the available information at hand, which the players will need to complete this game.
    \\

    Make sure you read this document completely before starting a game session, because it contains all the information you need to play.
    The quality of the game greatly depends on it, and it will make guiding the session just so much easier for you.
    \\

    \textbf{Should you be really short on time, make sure to read the \autoref{sec:storyboard_main}, \autoref{sec:game_setup} and all of the \enquote{Important Information} boxes in this file.
        This gives you the minimal amount of preparation needed.}
\end{hint}

The information is divided into different sections to give you the best possible overview of everything you need.
The most important thing, besides all the information provided, is how you pass it on to your players.
Your players will have a basic collection of the most important facts and events on their character sheets, so it's up to them to move the story forward.
But if they get stuck, need help, or have questions about the setting, it's you who can help them to move forward.
\\

You will need to balance how you feed them information.
You don't want to overdo it, since they need to be challenged to try and find out as much as possible on their own.
But you should prevent them from getting stuck or going in the completely wrong direction and losing time.
After all, this game should be finished in a reasonable amount of time.
\\

\begin{hint}[Important Information]
    Another thing before you start to read through this.
    Please keep in mind, that during the game some players will interact more with each other, while some will be more of the \enquote{quit observer} type.
    We feel that interaction is our games main learning point, so we advise you to make sure everybody tries to participate.
    You can do this by directly addressing specific participants with questions, or asking other participants if they have considered other opinions, etc.
    How you do it is up to you.
\end{hint}